Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-12 rates-neurips-21/rates.tex
started on property sectoin

\usepackage{amsmath,amsfonts}

@@

\DeclareMathOperator{\E}{\mathbb{E}}  % expectation

@@

@@

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}

@@

\subsection{Surrogate regrets and transfer rates}

%The primary focus of this paper is on surrogate regret bounds, which bound the excess target loss in terms of the excess surrogate loss.
%
%\begin{definition}[Regret]\label{def:regret}
%  For loss $L:\R\to\reals^\Y_+$ and distribution $p\in\simplex$, the \emph{regret} of a prediction $r\in\R$ is given by $R_L(r,p) = \inprod{p}{L(r)} - \risk{L}(p)$.
%\end{definition}
%

%
%
%\subsection{Property elicitation and consistency}
%
%Given a target problem specified by $\ell$, when is it appropriate to use a surrogate $L$?
%A key necessary condition is \emph{consistency} \bo{cite}, which roughly states that 
%
%
%We will assume throughout that the target loss is \emph{non-redundant}, meaning every report $r \in \R$ is uniquely optimal (uniquely minimizes expected loss) for some distribution $p\in\simplex$.
%$\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
%
%\begin{definition}[Property, level set]\label{def:property}
%  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
%  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r \defeq \{p \in \simplex : r \in \Gamma(p)\}$.
%\end{definition}
%
%\begin{definition}[Elicits]
%  \label{def:elicits}
%  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
%  \begin{equation}
%    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
%  \end{equation}
%  As $L$ elicits a unique property, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
%\end{definition}
%
%\begin{definition}[Embedding a loss]\label{def:loss-embed}
%  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
%  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
%  \begin{equation}\label{eq:embed-loss}
%    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
%  \end{equation}
%\end{definition}
%%
%

>>>>

\usepackage{amsmath,amsfonts,amssymb}

@@

\DeclareMathOperator{\E}{\mathbb{E}}  % expectation
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\arginf}{arg\,inf}

@@

\newcommand{\prop}[1]{\mathrm{prop}[#1]}

@@

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\toto}{\rightrightarrows}

@@

\subsection{Property elicitation and consistency}
Our technical approach is based on property elicitation, which studies the structure of $\ell$ and $L$ as they relate to $\simplex$.
In the below, $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.

\begin{definition}[Property, level set]\label{def:property}
  A \emph{property} is a function $\Gamma:\simplex\toto\R$.
  The \emph{level set} of $\Gamma$ for report $r$ is the set $\Gamma_r = \{p \in \simplex : r \in \Gamma(p)\}$.
\end{definition}

\begin{definition}[Elicits]
  \label{def:elicits}
  A loss $L:\R\to\reals^\Y_+$, \emph{elicits} a property $\Gamma:\simplex \toto \R$ if
  \begin{equation}
    \forall p\in\simplex,\;\;\;\Gamma(p) = \argmin_{r \in \R} \inprod{p}{L(r)}~.
  \end{equation}
  As $L$ elicits a unique property, we write $\prop{L}$ to refer to the property elicited by a loss $L$.
\end{definition}

\bo{Wrap this in an Assumption environment. I didn't think it fit well above...} We will assume throughout that the target loss is \emph{non-redundant}, meaning every report $r \in \R$ is uniquely optimal (uniquely minimizes expected loss) for some distribution $p\in\simplex$.

\begin{definition}[Embedding a loss]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
\end{definition}
